Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-04-10 paper/current/main.tex
add_ref
minor math edits

Then, we can rewrite the \ref{eq:gravity_model},
\begin{equation}
   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(\cos(v_i,v_j))
\end{equation}

@@

where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.  We use Skip-gram negative sampling, and following the work by Levy and Goldberg, it is implicitly factorizing

\begin{equation}
    \label{eq:sgns_relation}
    \log \left(\frac{\#(w,c) |D|}{\#(w) \#(c)} \right) - \log k
\end{equation}
where $\#(w)\text{,} \#(w) \text{ and } \#(c)$ denote the number of times word w, c and word-context-pair (w,c) in the corpus respectively. $k$ is the number of negative samples and $|D|$ is the size of the corpus. Eq. \ref{eq:sgns_relation} is symmetry matrix, result vector representation  $v_w$ and $v'_w$ are identical. With these relations, for a specific pair of words $(w_i, w_j)$,

@@

$|D|$ and k is constant, then it can be rewritten as

@@

Combining Eq. \ref{eq:approxi_mass_term}, we have

@@

It is consistent with the finding on our model, we can say that there is a mathematical link between the neural embedding model and the gravity model. Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.

>>>>

Then, we can rewrite Eq.~\ref{eq:gravity_model} as,
\begin{equation}
   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(\cos(v_i,v_j))
\end{equation}

@@

where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary.  We use Skip-gram negative sampling, and following the work by Levy and Goldberg \cite{levy2014neural}, consider the model as implicitely performing matrix factorization as shown below,

\begin{equation}
    \label{eq:sgns_relation}
    \log \left(\frac{\#(w,c) |D|}{\#(w) \#(c)} \right) - \log k
\end{equation}

where $\#(w)\text{, } \#(w) \text{ and } \#(c)$ denotes the number of times word $w$, $c$ and word-context-pair ($w$, $c$) in the corpus respectively. $k$ is the number of negative samples and $|D|$ is the size of the corpus. Eq. \ref{eq:sgns_relation} is symmetry matrix, result vector representation  $v_w$ and $v'_w$ are identical. With these relations, for a specific pair of words $(w_i, w_j)$,

@@

Where $|D|$ and $k$ are constants, such that the functional form can be re-written as,

@@

Combining Eq.~\ref{eq:approxi_mass_term}, we have

@@

This proportionality relationship is consistent with findings from our model, and so we can say that there is a mathematical link between the neural embedding model and the gravity model. Hence, the neural embedding model can be an effective model for investigating any kind of mobility trajectory data, stemming from the mathematical relationship between it and the gravity model of mobility.
